BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-02 tex/5-evaluation.tex
Eval++

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction success rates}
To evaluate of post content and title extraction we compared our approach to three open source projects: Readability\cite{}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{}. These projects are more generic than our blog specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of a same blog (assumptions \ref{havefeedAssum} and \ref{similarhtmlAssum}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content running time}

In addition to the quality of the extracted data we also evaluated the running time of the extraction procedure. The two point of interest are the time required to process a single page and the cumulated running time required to process multiple pages of a blog. The first result is significant for the \emph{UpdateCrawl} procedure, which is responsible for obtaining updates of already monitored blogs, and the second result regards the \emph{NewCrawl} procedure triggered when a new blog is added to the system and all previously published content has to be processed.

Our measurements were made with garbage collector disabled on a otherwise idle core of a \TODO{Intel X} processor.  asdjf élaksd jfélkas jfélkas jfélaskjd félakjd fékas jfdéasdj féaksd jf

% rtime eval, scalability with size of blogs

% rsetup (single core, gc disabled, measure time spent in respective extraction functions)

% result (plot)

\input{runningtimeFigure.tex}

% discussion: again, we are "cheating" on scalability
% discussion: raw perf (15 feed entry),
% discussion: (c++ vs java vs scala vs go \cite{hundt2011})Implemented in Javascript, Java and Scala respectively

>>>>

% All experiments are reproducable by following instructions on the \emph{evaluation} branch of the BlogForever-Crawler version control **.
% https://github.com/OlivierBlanvillain/blogforever-crawler-publication

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction success rates}
To evaluate of post content and title extraction we compared our approach to three open source projects: Readability\cite{}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{}. These projects are more generic than our blog specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of a same blog (assumptions \ref{havefeedAssum} and \ref{similarhtmlAssum}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content extraction running times}

% running time eval, scalability with size of blogs
In addition to the quality of the extracted data we also evaluated the running time of the extraction procedure. The main point of interest will be the scalability of extraction procedures as the number of processes pages increases. This corresponds to the evaluation of a \emph{NewCrawl} task, which is in charge of harvesting all previously published data on a blog.

% setup
Our measurements were made with garbage collector disabled on a otherwise idle core of an \TODO{Intel X} processor. Experimental data where obtained by taking the median of 11 mesurements. confidence intervals .. in .. as (max 0.002 sec)

Figure 2 shows the cumulated time spent on each content extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of process blog posts on the \surl{http://quantumdiaries.org/} website.

% result (plot)
\input{runningtimeFigure.tex}

% discussion: again, we are "cheating" on scalability

% discussion: raw perf (15 feed entry),
% discussion: (c++ vs java vs scala vs go \cite{hundt2011})Implemented in Javascript, Java and Scala respectively
% YUNO algo 2
